\documentclass[a4paper,oneside,english]{article}

\usepackage{geometry}
\geometry{layouthoffset=.3in,marginparwidth=20.5in,marginparsep=21pt,textwidth=5.7in,textheight=8in,top=1in,bottom=1in,footskip=0in}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{cite}
\usepackage{url}
\usepackage{microtype}
\usepackage{multibib}
\usepackage{babel}
\usepackage{marginnote}
\usepackage{setspace}
\usepackage[absolute]{textpos}
\setlength{\TPHorizModule}{1mm}
\setlength{\TPVertModule}{1mm}
\renewcommand*{\marginfont}{\normalfont\normalsize}
\def\labelitemi{--}
	
\begin{document}
\pagenumbering{gooble}

\begin{textblock}{50}(15,9)
	\noindent \textbf{\huge Abhinav Jauhri}  \\ \\
        \rule{7in}{0.4pt}
\end{textblock}

\begin{textblock}{50}(145,9)
	\noindent Email: ajauhri@cmu.edu  \\
	\noindent \url{http://abhinavjauhri.com} \\
\end{textblock}

\reversemarginpar
\marginnote{Education} 
\noindent \textbf{Carnegie Mellon University}, Pittsburgh, PA.  \\ PhD in Computer Engineering, August, 2012 - Present. \\ Advisor: Jason Lohn  \vspace*{2mm} \\
\textbf{Carnegie Mellon University}, Pittsburgh, PA. \\ MS in Software Engineering, 2011. \vspace*{2mm} \\
\textbf{Narsee Monjee University}, Mumbai, India. \\ B.Tech. in Computer Engineering, 2010. \\
\noindent\rule{6in}{0.4pt}  \\[4pt]
\marginnote{Research \\Interests} 
\noindent My interests lie in the areas of systems, machine learning and optimization. Specifically, I am interested in applying optimization techniques with applications to computer system design. \\
\noindent\rule{6in}{0.4pt} \\[4pt]
\marginnote{Papers under \\Submission And \\Working Papers} 
\textit{Recommendations Using Coupled Matrix Factorization}, Evangelos Papalexakis, Abhinav Jauhri. PAKDD 2014, Tainan, Taiwan. Submitted in October, 2013. \vspace*{2mm} \\
\textit{Measuring Client Device Behavior on the Modern Web}, Erik Reed, Abhinav Jauhri. NIPS 2013. Submitted in October, 2013. \\
\textit{ }
\noindent\rule{6in}{0.4pt} \\[4pt]
\marginnote{Professional \\Employment} \textbf{Software Engineer}, Salesforce.com Inc., San Francisco, CA, (September, 2011 - July, 2012)
\begin{itemize}
	\itemsep0em
	\item Created APIs for report generation for different entities within the commerce platform. 
	\item Developed and modeled a platform to enable commerce activities across products.
\end{itemize}
\noindent\rule{6in}{0.4pt} \\[4pt]
\marginnote{Graduate \\Assistantships} \textbf{Optimization Algorithms for Antenna Placement}, Carnegie Mellon University (September, 2010 - August, 2011) 
\begin{itemize}
	\itemsep0em
	\item Developed stochastic algorithms to locate near-optimal antenna placements.
	\item Contributed in design and implementation of evolutionary algorithms: Genetic Algorithm, Simulated Annealing, Hill Climber.
\end{itemize} \vspace*{2mm}
Formulated course, \textbf{How to Write Fast Code (18-645)}, Carnegie Mellon University (May, 2011 - August, 2011) 
\begin{itemize}
	\itemsep0em
	\item Prepared class assignments using CUDA, OMP, and Hadoop.
	\item Prepared infrastructure for students to collaborate, and test code on clusters.
\end{itemize}
\noindent\rule{6in}{0.4pt} \\[4pt]
\marginnote{Summer \\Internships} \textbf{Nvidia}, Santa Clara, CA. Summer 2013. 
\begin{itemize}
	\itemsep0em
	\item Worked on adding functionalities in C++ to provide video streaming for their gaming platform. 
	\item Developed a thread pool library for Windows platform. 
\end{itemize} \vspace*{2mm}
\noindent\textbf{Red Hat}, Pune, India. Summer 2009.
\begin{itemize}
	\itemsep0em
	\item Worked on a converged VoIP conference application for GNU/Linux platform. The web based application used Session Initiation Protocol (SIP) for session management. 
	\item Developed a mechanism to allow persistence storage of users logged onto the VoIP application to enable conferencing using Real-time Transport Protocol (RTP). \url{http://code.google.com/p/jvprism}
\end{itemize}
\noindent\rule{6in}{0.4pt} \\[4pt]
\marginnote{Projects} 
\textbf{Binomial and Fibonacci heaps in Racket}, for submission at \href{http://lispinsummerprojects.org/}{Lisp In Summer Projects, 2013}
\begin{itemize}
	\itemsep0em
	\item Functional implementation of heaps using dialect of Lisp.
	\item Benchmarked and compared with existing libraries in Racket. \url{https://github.com/ajauhri/rkt-heaps}  
\end{itemize} \vspace*{2mm}
\noindent\textbf{Measuring Client Device Behavior on the Modern Web}, Carnegie Mellon University (January, 2013 - May, 2013)
\begin{itemize}
	\itemsep0em
	\item Our hypothesis - Most of the client devices have workload which require fetching of state information from a remote server. Understanding the access pattern is essential to perform optimizations.
	\item Collecting and analyzing patterns of popular websites and web-based applications. \url{https://github.com/ajauhri/web-stap} 
\end{itemize} \vspace*{2mm}
\noindent\textbf{Evograph}, Carnegie Mellon University (January, 2011 - April, 2011)
\begin{itemize}
	\itemsep0em
	\item Developed evolutionary algorithms to represent graphs aesthetically.
	\item Assessed performances of different algorithms on complete graphs. \url{http://code.google.com/p/evograph}
\end{itemize} \vspace*{2mm}
\noindent\textbf{Process Enactment Tool}, Carnegie Mellon University (August, 2010 - December, 2010)
\begin{itemize}
	\itemsep0em 
	\item Developed a tool using Ruby on Rails to effectively track processes in a software organization. Extreme Programming (XP) was adopted in the course of its development. Test Driven Development (TDD) was accomplished using RSpec. Selenium was used for creating integration tests.
	\item Worked on the design and development of core functionalities, and developed the test suite. \url{http://github.com/ajauhri/Fall-2010-Public}
\end{itemize} \vspace*{2mm}
\noindent\textbf{Distributed Storage Systems}, Narsee Monjee University (July, 2009 - May, 2010)
\begin{itemize}
	\itemsep0em
	\item Designed and implemented an application to allow storage of data on multiple nodes in a network. 
	\item Worked on the implementation of a virtual file system layer using FUSE-J to intercept system calls, and perform customized operation. Also, developed protocols to enable interaction between storage nodes. \url{http://distrosys.wikia.com}
\end{itemize} \vspace*{2mm}
\noindent\textbf{Packet Sniffer}, Narsee Monjee University (January, 2009 - March, 2009)
\begin{itemize}
	\itemsep0em
	\item Created a system to capture, store, and analyze network packets. An initial version of a Honey-Pot architecture was developed.
\end{itemize} \vspace*{2mm}
\noindent\textbf{IT Enabled Academia}, representing Narsee Monjee University at IBM's Great Mind Challenge 2008
\begin{itemize}
	\itemsep0em
	\item Built an application to provide a framework for educational institutions to automate their administrative mechanisms with the conventional student-faculty interactions. Some key features included time-table generation, exchange of study material, archival of student’s data, report generation, and bar-code generator.
	\item Worked on development of all functionalities, database schema design, and XQueries. \url{http://github.com/ajauhri/itea}
\end{itemize}
\noindent\rule{6in}{0.4pt} \\[4pt]
\marginnote{Graduate \\Coursework}
Stochastic Optimization by \href{https://www.cmu.edu/silicon-valley/faculty-staff/lohn-jason.html}{\UrlFont Jason Lohn} \vspace*{2mm} \\  
Analytical Performance Modeling \& Design of Computer System by \href{https://www.cs.cmu.edu/~harchol/Perfclass/class12fall.html}{\UrlFont Mor Harchol-Balter}  \vspace*{2mm} \\
Machine Learning by \href{http://alex.smola.org/teaching/cmu2013-10-701/}{\UrlFont Alex Smola \& Barnabas Poczos}  \vspace*{2mm} \\
Graduate Algorithms by \href{https://www.cs.cmu.edu/~mblum/}{\UrlFont Manuel Blum}  \vspace*{2mm} \\
Advanced and Distributed Operating Systems by \href{https://www.cs.cmu.edu/~15712/}{\UrlFont Hui Zhang}

\noindent\rule{6in}{0.4pt} \\[4pt]
\marginnote{Systems \\Experience} 
Programming Languages: C, C++, Java, Racket, Matlab \vspace*{2mm}  \\
Scripting Languages: Python, bash, Javascript \vspace*{2mm} \\ 
RDBMS Language: SQL \vspace*{2mm} \\  
DBMS: DB2, Oracle 9i, MySQL, SQLite \vspace*{2mm} \\ 
Presentation technologies: HTML, \LaTeX \\
\noindent\rule{6in}{0.4pt} \\[4pt]
\marginnote{Selected \\Honors}
Carnegie Institute of Technology Dean's Tuition Fellowship for academic year 2012 - 13. \vspace*{2mm} \\
Head of Editorial Board at Narsee Monjee University for academic year 2009 - 10. \vspace*{2mm} \\
\noindent Member of a team which was amongst best 20 teams selected fromm all over India by IBM at their annual competition, Great Mind Challenge, 2008. \vspace*{2mm} \\
Chairperson of the Student Branck of Computer Society of India (CSI) at Narsee Monjee University for academic year 2007 - 08.  \vspace*{2mm} \\
College prefect at La Martiniere College, Lucknow, India for academic year 2005 - 06.
\end{document}
